---
title: "Exploration of Animal Telemetry Data"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: menu
    source_code: https://github.com/ValleLabUF/segment_continuous_var
    theme: journal
---
<style>
.navbar-inverse {
  background-color: blue;
  border-color: white;
}

.navbar-inverse .navbar-brand:hover,
.navbar-inverse .navbar-brand:focus {
  color: white;
  background-color: #FF7F00;
}

.navbar-inverse .navbar-nav > li > a:hover,
.navbar-inverse .navbar-nav > li > a:focus {
  color: white;
  background-color: #FF7F00;
}

.navbar-inverse .navbar-nav > .active > a,
.navbar-inverse .navbar-nav > .active > a:hover,
.navbar-inverse .navbar-nav > .active > a:focus {
  color: white;
  background-color: #FF7F00;
}
</style>



```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(dplyr)
library(purrr)
library(sf)
library(sp)
library(rgdal)
# library(raster)
library(viridis)
library(rgeos)
# library(tidyr)
library(leaflet)
# library(highcharter)
# library(bayesmove)
library(lubridate)
# library(plotly)
library(dygraphs)
library(xts)
library(shinyWidgets)

#####################
#### Import data ####
#####################

# dat<- read.csv("Snail Kite Gridded Data_TOHO_R2n.csv", header = T, sep = ",")
# 
# dat$id<- as.character(dat$id)
# dat$date<- as_datetime(dat$date)
# 
# 
# #make reactive NSD data
# dat.filt<- reactive({
#   
# d<- dat[dat$id == input$animal_id, ]
# return(d)
# })

#Allow users to upload up to 30 MB at a time
options(shiny.maxRequestSize = 30*1024^2)

#make uploaded data (csv) reactive
dat<- reactive({
    req(input$filedata)
    dat<- read.csv(input$filedata$datapath)
    
    dat$id<- as.character(dat$id)
    dat$date<- as_datetime(dat$date)
    
    return(dat)
  })




```





Explore data
======================================================================

Sidebar {.sidebar}
-----------------------------------------------------------------------
<style>
.section.sidebar {
  top: 61px;
  background-color: rgba(255, 127, 0, 0.25);
}
</style>

```{r}
# Define inputs
fileInput(inputId = "filedata",
          label = "Choose a CSV file",
          multiple = TRUE,
          accept = c(".csv"))

numericInput(inputId = "epsg",
             label = "Enter EPSG",
             value = 4326)

actionButton('update' ,'Load Data')

selectInput('animal_id', label = 'Select an ID', choices = NULL)

selectInput('var', label = 'Select a Variable', choices = NULL)


```

Use the __Explore data__ tab to explore temporal patterns of user selected variables from the loaded CSV file for each ID in the dataset. **Only CSV files can be loaded at  this time.** At minimum, the file must have columns labeled `id`, `x`, `y`, and `date`, but can accommodate any others. The `date` column must be stored in POSIXct format (i.e., YYYY-MM-DD). Click and drag on the lineplot to highlight the corresponding time range on the neighboring map.

Additionally, the projection of these locations must also be provided (as EPSG) to be mapped. If coordinates stored as longitude and latitude, use *4326* for EPSG. For more information on EPSG codes, please refer to this [link](https://epsg.io).

Click the __View all tracks__ tab to view tracks for all individuals. This provides a quick overview of all track segments separately and allows for filtering tracks by time.

Application author: [Josh Cullen](https://joshcullen.github.io/), [University of Florida](http://www.ufl.edu)





Row
-----------------------------------------------------------------------

### Time-Series Analysis

```{r}


#Update selectInput
observeEvent(dat(), {
  updateSelectInput(session, "animal_id", choices = unique(dat()$id),
            selected = unique(dat()$id)[1])
  
  updateSelectInput(session, "var", choices = names(dat())[-which(names(dat()) == "id")],
            selected = names(dat())[-which(names(dat()) == "id")][1])
})

#Filter by ID
dat.filt <- reactive({
  
  if (!is.null(dat())) {
    d<- dat()[dat()$id == input$animal_id, ]
  } else {
    d<- NULL
  }
  
    return(d)
  })




output$lineplot<- renderDygraph({
  
  # dat.plot<- ifelse(length(stringr::str_detect(dat.filt()[1:2,input$var],
  #                                                 c(letters,LETTERS))) > 0,
  #                      as.numeric(factor(dat.filt()[,input$var])),
  #                      dat.filt()[,input$var])

  
dygraph(xts(x = dat.filt()[,input$var], order.by = dat.filt()$date)) %>%
    dySeries(label = input$var, strokeWidth = 1.5) %>% 
    dyAxis("y", label = input$var, axisLabelFontSize = 16, axisLabelWidth = 75) %>%
    dyRangeSelector(dateWindow = NULL) %>% 
    dyOptions(axisLineWidth = 1.5, drawGrid = FALSE, colors = "black") %>% 
    dyLegend(width = 270) %>% 
    # dyShading(from = "2018-03-01", to = "2018-06-30") %>%
    # dyShading(from = "2019-03-01", to = "2019-06-30") %>% 
    dyUnzoom() %>% 
    dyCrosshair(direction = "vertical")
    
})


reacted.data<- reactive({
  req(input$lineplot_date_window)  #to prevent warning from 'if' expression
  
  start=strptime(input$lineplot_date_window[[1]], format = "%Y-%m-%dT%H:%M:%S", tz = "UTC")
  end=strptime(input$lineplot_date_window[[2]], format = "%Y-%m-%dT%H:%M:%S", tz = "UTC")

    if (start == min(dat.filt()$date) & end == max(dat.filt()$date)){
      dat.filt()
    } else {
      subset = dplyr::filter(dat.filt(), date >= start & date <= end)
      return(subset)
    }
  })



dygraphOutput("lineplot")

```



### Track Map

```{r}
# Draw the map without selected tracks
output$map <- renderLeaflet({

    # bounds<- reactive({
    #   dat.sf<- st_as_sf(dat.filt(), coords = c("x","y"), crs = input$epsg) %>%
    #     st_transform(4326)
    #   extent<- as.numeric(st_bbox(dat.sf))
    # 
    #   return(extent)
    # })


    leaflet(options = leafletOptions(preferCanvas = TRUE)) %>%
    addProviderTiles(providers$Esri.OceanBasemap, group = "Ocean Basemap",
                        options = tileOptions(continuous_world = F)) %>%
    addProviderTiles(providers$Esri.WorldImagery, group = "World Imagery",
                        options = tileOptions(continuous_world = F)) %>%
    addProviderTiles(providers$CartoDB.DarkMatterNoLabels, group = "Dark Map",
                        options = tileOptions(continuous_world = F)) %>%
    setView(lng = -96, lat = 37, zoom = 4) %>%
    addMeasure(position = "topleft",
               primaryLengthUnit = "kilometers",
               primaryAreaUnit = "hectares",
               activeColor = "#3D535D",
               completedColor = "#7D4479") %>%
    addMiniMap(tiles = providers$Esri.OceanBasemap,
               toggleDisplay = TRUE,
               position = "bottomleft") %>%
      addScaleBar() %>%
      addLayersControl(baseGroups = c("World Imagery", "Ocean Basemap", "Dark Map"),
                   options = layersControlOptions(collapsed = TRUE))
  })


####---------------------------------------------------

toListen <- reactive({
    list(input$update, reacted.data())
  })

observeEvent(toListen(), {
  
# UPDATED MAP
  req(reacted.data()) # Do this if reacted.data() is not null
#
#   #set palette
#   # pal1<- colorNumeric(palette = "Spectral", domain = dat.filt()$tseg)
#   # pal1.rev<- colorNumeric(palette = "viridis", domain = dat.filt()$tseg, reverse = T)
#

  dat.filt.sf<- st_as_sf(dat.filt(), coords = c("x","y"), crs = input$epsg) %>%
      st_transform(4326) %>%
      st_cast("LINESTRING")

  df<- reactive({
    df<- reacted.data()

    dat.sf<- st_as_sf(df, coords = c("x","y"), crs = input$epsg) %>%
      st_transform(4326) %>%
      # summarize(do_union = FALSE) %>%
      st_cast("LINESTRING") #%>%
      # mutate(x = unlist(map(.$geometry,1)),
      #        y = unlist(map(.$geometry,2))) %>%
      # st_drop_geometry()

    dat.sf

  })


  df.start.pt<- reactive({
    df<- reacted.data()

    dat.sf<- sf::st_as_sf(df, coords = c("x","y"), crs = input$epsg) %>%
       sf::st_transform(4326) %>%
       # summarize(do_union = FALSE) %>%
       # st_cast("POINT") %>%
       dplyr::slice(1)

    dat.sf

  })

  df.end.pt<- reactive({
    df<- reacted.data()

    dat.sf<- sf::st_as_sf(df, coords = c("x","y"), crs = input$epsg) %>%
       sf::st_transform(4326) %>%
       # summarize(do_union = FALSE) %>%
       # st_cast("POINT") %>%
       dplyr::slice(nrow(df))

    dat.sf

  })




  # Clear old selection on map, and add new selection
  leafletProxy('map', data = df()) %>%
  clearControls() %>%
  clearShapes() %>%
  clearMarkers() %>%
  fitBounds(as.numeric(sf::st_bbox(df())[1]),
            as.numeric(sf::st_bbox(df())[2]),
            as.numeric(sf::st_bbox(df())[3]),
            as.numeric(sf::st_bbox(df())[4])) %>%
  addPolylines(lng = as.numeric(sf::st_coordinates(dat.filt.sf)[,1]),
               lat = as.numeric(sf::st_coordinates(dat.filt.sf)[,2]),
               weight = 2,
               color = "lightgrey",
               opacity = 0.4) %>%
  addPolylines(lng = as.numeric(sf::st_coordinates(df())[,1]),
               lat = as.numeric(sf::st_coordinates(df())[,2]),
               weight = 2,
               color = "darkturquoise",
               opacity = 0.8) %>%
  addCircleMarkers(data = df.start.pt(),
                   # lng = as.numeric(sf::st_coordinates(df.start.pt())[,1]),
                   # lat = as.numeric(sf::st_coordinates(df.start.pt())[,2]),
                   fillColor = "#5EF230",
                   stroke = FALSE,
                   fillOpacity = 0.8) %>%
  addCircleMarkers(data = df.end.pt(),
                   # lng = as.numeric(sf::st_coordinates(df.end.pt())[,1]),
                   # lat = as.numeric(sf::st_coordinates(df.end.pt())[,2]),
                   fillColor = "red",
                   stroke = FALSE,
                   fillOpacity = 0.8)

})

leafletOutput('map')
```



View all tracks
======================================================================

Sidebar {.sidebar}
-----------------------------------------------------------------------
<style>
.section.sidebar {
  top: 61px;
  background-color: rgba(255, 127, 0, 0.25);
}
</style>

<br />
```{r}

pickerInput(
   inputId = "select_ids",
   label = "Select/deselect by ID", 
   choices = NULL,
   options = list(
      `actions-box` = TRUE), 
    multiple = TRUE
)

```
<br />


Use the __Explore data__ tab to explore temporal patterns of user selected variables from the loaded CSV file for each ID in the dataset. **Only CSV files can be loaded at  this time.** At minimum, the file must have columns labeled `id`, `x`, `y`, and `date`, but can accommodate any others. The `date` column must be stored in POSIXct format (i.e., YYYY-MM-DD). Click and drag on the lineplot to highlight the corresponding time range on the neighboring map.

Additionally, the projection of these locations must also be provided (as EPSG) to be mapped. If coordinates stored as longitude and latitude, use *4326* for EPSG. For more information on EPSG codes, please refer to this [link](https://epsg.io).

Click the __View all tracks__ tab to view tracks for all individuals. This provides a quick overview of all track segments separately and allows for filtering tracks by time.

Application author: [Josh Cullen](https://joshcullen.github.io/), [University of Florida](http://www.ufl.edu)


Row {data-height=150, align="center"}
-----------------------------------------------------------------------

### Dates

<style>
.irs-bar {width: 100%; height: 10px;}
.irs-line {border: 1px solid black; height: 10px; border-radius: 0px;}
      .irs-max {font-family: 'arial'; color: black;}
      .irs-min {font-family: 'arial'; color: black;}
      .irs-single {color:black; background:#6666ff;}
      .irs-grid-text {font-size: 12pt; color: black}
      
</style>

```{r}

# Define inputs
div(style="width: 1000px; ", sliderInput("range", NULL,
                  min = NULL, max = NULL,
                  value = c(0,1), width = '100%', step = 90))
  
```


Row {data-height=850}
-----------------------------------------------------------------------

### Map of All Tracks

```{r}

observeEvent(input$update, {
  updatePickerInput(session, "select_ids", choices = unique(dat()$id),
   selected = unique(dat()$id))
  
  updateSliderInput(session, "range", min = min(dat()$date), max = max(dat()$date),
                  value = range(dat()$date))
})




#store data as list after clicking "Load data" button
dat.list<- reactive({
  d.list<- split(dat(), dat()$id)  #split data into list by ID
  d2<- bind_rows(d.list[input$select_ids])  #only keep selected IDs
  
  return(d2)
})

  #make reactive data based on slider input
dat.filt2<- reactive({
  dat<- dat.list()
  dat<- dat[dat$date >= input$range[1] & dat$date <= input$range[2], ]  #only keep w/in range

  #format data where each ID is a linestring
  dat.sf<- st_as_sf(dat, coords = c("x","y"), crs = input$epsg) %>%
             st_transform(4326) %>%
             group_by(id) %>%
             summarize(do_union=F) %>%
             st_cast("LINESTRING")
  # if (is.null(dat.list())) return(NULL)

  return(dat.sf)
})





# Create basemap
output$map_all <- renderLeaflet({
  
  #set palette
    pal1<- colorFactor(palette = "viridis", domain = dat.filt2()$id)

    labs<- sprintf("<strong>ID %s</strong><br/>", dat.filt2()$id) %>%
       lapply(htmltools::HTML)


    leaflet(data = dat.filt2()) %>%
    addProviderTiles(providers$Esri.OceanBasemap, group = "Ocean Basemap",
                        options = tileOptions(continuous_world = F)) %>%
    addProviderTiles(providers$Esri.WorldImagery, group = "World Imagery",
                        options = tileOptions(continuous_world = F)) %>%
    addProviderTiles(providers$CartoDB.DarkMatterNoLabels, group = "Dark Map",
                        options = tileOptions(continuous_world = F)) %>%
    clearControls() %>%
    clearShapes() %>%
    fitBounds(as.numeric(sf::st_bbox(dat.filt2())[1]),
          as.numeric(sf::st_bbox(dat.filt2())[2]),
          as.numeric(sf::st_bbox(dat.filt2())[3]),
          as.numeric(sf::st_bbox(dat.filt2())[4])) %>%
      addPolylines(data = dat.filt2(),
               weight = 2,
               # layerId = ~unique(id),
               color = ~pal1(id),
               label = labs) %>%
      leaflet::addLegend("bottomright",
               pal = pal1,
               values = dat.filt2()$id,
               title = "ID",
               opacity = 1) %>% 
      addMiniMap(tiles = providers$Esri.OceanBasemap,
               toggleDisplay = TRUE,
               position = "bottomleft") %>%
      addScaleBar() %>%
      addLayersControl(baseGroups = c("Ocean Basemap", "World Imagery", "Dark Map"),
                   options = layersControlOptions(collapsed = TRUE), position = "topleft")
})


leafletOutput('map_all')
```




